%
% General structure for the revdetua class:
%
\documentclass[shortpaper,english,final]{revdetua}
%
% Valid options are:
%
%   longpaper --------- \part and \tableofcontents defined
%   shortpaper -------- \part and \tableofcontents not defined (default)
%
%   english ----------- main language is English (default)
%   portugues --------- main language is Portuguese
%
%   draft ------------- draft version
%   final ------------- final version (default)
%
%   times ------------- use times (postscript) fonts for text
%
%   mirror ------------ prints a mirror image of the paper (with dvips)
%
%   visiblelabels ----- \SL, \SN, \SP, \EL, \EN, etc. defined
%   invisiblelabels --- \SL, \SN, \SP, \EL, \EN, etc. not defined (default)
%
% Note: the final version should use the times fonts
% Note: the really final version should also use the mirror option
%

\usepackage{amsmath,hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{titlesec}
\algnewcommand{\Inputs}[1]{%
  \State \textbf{Inputs:}
  \Statex \hspace*{\algorithmicindent}\parbox[t]{.8\linewidth}{\raggedright #1}
}
\algnewcommand{\Initialize}[1]{%
  \State \textbf{Initialize:}
  \Statex \hspace*{\algorithmicindent}\parbox[t]{.8\linewidth}{\raggedright #1}
}
\newcommand{\algorithmautorefname}{Algorithm}

\titleclass{\section}{straight}

\begin{document}

\Header{1}{1}{Janeiro}{2023}{1}
% Note: the month must be in Portuguese

\title{On the usage of approximate counters for the occurrences of words}
\author{Manuel Gomes, 88939} % or \author{... \and ...}
\maketitle

\begin{abstract}% Note: in English
This report present four algorithms to solve a minimum weight dominating set graph problem.
The first one is an exhaustive search algorithm, while the rest are based on greedy heuristics.
A formal analysis is presented for each algorithm.
After their implementation in Python 3, an experimental analysis of each algorithm is described.
\end{abstract}

\begin{resumo}% Note: in Portuguese
Este relatório apresenta quatro algoritmos com o objetivo resolver o problema de grafos "minimum weight dominating set".
O primeiro é um algoritmo de procura extensiva, enquanto que o resto são baseados em heurísticas vorazes.
Uma análise formal é apresentada para cada algoritmo.
Após a sua implementação em Python 3, uma análise experimental de cada algoritmo é descrita.
\end{resumo}

% \begin{keywords}% Note: in English (optional)
%   ...
% \end{keywords}

% \begin{palavraschave}% Note: in Portuguese (optional)
%   ...
% \end{palavraschave}


\input{src/01-introduction}
\input{src/02-algorithms-used}
\input{src/03-results}
\input{src/04-conclusions}

% \bibliography{references.bib}
% \bibliography{...} % use a field named url or \url{} for URLs
% Note: the \bibliographystyle is set automatically

\end{document}
